A general framework for learning planning action models

### 2018-06-14 doc/aij18/background.tex

\AMAN uses the same metric as \LAMP, namely counting the number of preconditions and effects that appear in the learned model and not in the ground-truth model (extra fluents) and viceversa (missing fluents). In a comparison between \AMAN and \ARMS on noiseless inputs, the results show that the accuracy performance of both \AMAN and \ARMS are very close to each other and neither dominates the other. The convergence property of \AMAN guarantees that the accuracy of the learned model with noisy input traces becomes more and more close to the case  \emph{without noise} because the distribution of noise in the plan becomes gradually closer to real distribution with the number of iterations.

>>>>

\AMAN uses the same metric as \LAMP, namely counting the number of preconditions and effects that appear in the learned model and not in the ground-truth model (extra fluents) and viceversa (missing fluents). In a comparison between \AMAN and \ARMS on noiseless inputs, the results show that the accuracy of the learnt models are very close to each other and neither dominates the other. The convergence property of \AMAN guarantees that the accuracy of the learned model with noisy input traces becomes more and more close to the case  \emph{without noise} because the distribution of noise in the plan becomes gradually closer to real distribution with the number of iterations.
